The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2016-03-16 script/de/script-de.tex
CT Book ed 12: New cover page

% Define title ......................
% \title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
% \title{\vspace{25pt}
\title{
% be_Wished to enlarge only the main title, however \HUGE not available,
%    or \HUGE without any effect beside adding \usepackage[11pt]{moresize}
%    and explicit use of \fontsize caused the LaTeX Font Warning:
%    Font shape `OT1/cmr/m/n' in size <40> not available size <24.88> substituted on input line 130.
%    {\usefont{\encodingdefault}{\rmdefault}{b}{n}%
%     \fontsize{40}{48} \selectfont Das CrypTool-Buch}
%    {\fontsize{40}{48} \selectfont Das CrypTool-Buch} \\[15pt]
%    {\HUGE Das CrypTool-Buch} \\[15pt]
% --> Später: Use the KOMA-script class or the memoir class (erfordert aber andere \documentclass)
%             http://texblog.org/2012/08/29/changing-the-font-size-in-latex/
	{\Huge Das CrypTool-Buch \\[15pt]
	       Kryptographie, Mathematik und mehr} \\[25pt]
	{\LARGE Hintergrundmaterial und Zusatzinformationen\\
	 zum freien E-Learning Krypto-Programm CrypTool\\[5pt]
	 (mit Code-Beispielen, geschrieben in SageMath)} \\[25pt]
	%{\large 12. Auflage}
	{\large 12. Auflage -- Draft-Version (\settimeformat{hhmmsstime}\currenttime)}
        \vspace{180pt}
}

@@

% \includepdf[pages=1]{figures/coverv1_de-300dpi.pdf}
% \includepdf[pages=1]{figures/coverv1_de.pdf}
\includepdf[pages=1]{figures/coverv1_de_draft.pdf}

@@

\maketitle

>>>>

% Define title ......................
% \title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
% \title{\vspace{25pt}
\title{%
% be_Wished to enlarge only the main title, however \HUGE not available,
%    or \HUGE without any effect beside adding \usepackage[11pt]{moresize}
%    and explicit use of \fontsize caused the LaTeX Font Warning:
%    Font shape `OT1/cmr/m/n' in size <40> not available size <24.88> substituted on input line 130.
%    {\usefont{\encodingdefault}{\rmdefault}{b}{n}%
%     \fontsize{40}{48} \selectfont Das CrypTool-Buch}
%    {\fontsize{40}{48} \selectfont Das CrypTool-Buch} \\[15pt]
%    {\HUGE Das CrypTool-Buch} \\[15pt]
% --> Später: Use the KOMA-script class or the memoir class (erfordert aber andere \documentclass)
%    http://texblog.org/2012/08/29/changing-the-font-size-in-latex/
	{\Huge ~ \\[20pt]
	       Das CrypTool-Buch:\\[20pt]
	       Kryptographie lernen und anwenden\\[15pt]
               mit CrypTool und SageMath} \\[25pt]
	{\LARGE Hintergrundmaterial und Zusatzinformationen\\
	 zum freien E-Learning Krypto-Programm CrypTool\\[5pt]
	 (Kryptographie, Mathematik und mehr)} \\[25pt]
	%{\large 12. Auflage}
	{\large 12. Auflage -- Draft-Version (\settimeformat{hhmmsstime}\currenttime)}
        \vspace{180pt}
}

@@

% \includepdf[pages=1]{figures/coverv1_de-300dpi.pdf}
\includepdf[pages=1]{figures/coverv1_de.pdf}
% \includepdf[pages=1]{figures/coverv1_de_draft.pdf}

@@

% TODO: Warum nach dem Cover eine leere Seite und auf der von \maketitle
%       erstellten 3. Seite die Seitennummer II ?  Beides ist akzeptabel.
% TODO: Warum beginnt er auf der 4. Seite wieder mit der Seite römisch I ?
%       Das sollte nicht sein!
\maketitle

### 2016-03-16 script/en/script-en.tex
Corrected typos and overfull hbox; congruent index (no redundancy in wording; adjectives in lowercase in German; all normal words in lowercase in English)
CT Book ed 12: New cover page

% Define title ..............
\title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
	{\Huge The CrypTool Book \\[15pt]
         Cryptography, Mathematics, and More} \\[25pt]
	{\LARGE	Background reading for CrypTool\\ 
         the free e-learning crypto program \\[5pt]
	 (with code samples written in SageMath)} \\[25pt]
	{\large 12th edition -- draft version (\settimeformat{hhmmsstime}\currenttime)}
	% {\large 12th edition}
        \vspace{180pt}
}

@@

% \includepdf[pages=1]{figures/coverv1_en-300dpi.pdf}
% \includepdf[pages=1]{figures/coverv1_en.pdf}
\includepdf[pages=1]{figures/coverv1_en_draft.pdf}

@@

\maketitle

@@

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{List of SageMath Code Examples}
\listof{sagecode}{List of SageMath Code Examples}
\index{SageMath!Code examples}
\label{sc:List-of-Sage-Code-Examples}

>>>>

% Define title ..............
\title{% Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
	{\Huge ~ \\[20pt]
	 The CrypTool Book: \\[20pt]
         Learning and Experiencing\\[15pt]
         Cryptography\\[20pt]
         with CrypTool and SageMath} \\[25pt]
	{\LARGE	Background reading for CrypTool\\ 
         the free e-learning crypto program \\[5pt]
	 (Cryptography, Mathematics, and More)} \\[25pt]
	{\large 12th edition -- draft version (\settimeformat{hhmmsstime}\currenttime)}
	% {\large 12th edition}
        \vspace{180pt}
}

@@

% \includepdf[pages=1]{figures/coverv1_en-300dpi.pdf}
\includepdf[pages=1]{figures/coverv1_en.pdf}
% \includepdf[pages=1]{figures/coverv1_en_draft.pdf}

@@

\vspace{30pt}
\maketitle

@@

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{List of SageMath Code Examples}
\listof{sagecode}{List of SageMath Code Examples}
\index{SageMath!code examples}
\label{sc:List-of-Sage-Code-Examples}
